\begin{thebibliography}{99}
\addcontentsline{toc}{section}{References}

\bibitem{tabor2020modern} 
Tabor P. (2020).
\textit{Modern Reinforcement Learning: Deep Q Learning in Pytorch.} 
\texttt{https://www.udemy.com/course/deep-q-learning-from-paper-to-code}

\bibitem{sutton2018reinforcement} 
Sutton R. S., Barto A. G. (2018).
\textit{Reinforcement Learning: An Introduction (second edition).}
MIT Press, Cambridge, MA.
\texttt{http://incompleteideas.net/book/the-book-2nd.html}

\bibitem{hessel2017rainbow} 
Hessel M., Modayil J., van Hasselt H., Schaul T., Ostrovski G., Dabney W., Horgan D., Piot B., Azar M., Silver D. (2017).
\textit{Rainbow: Combining Improvements in Deep Reinforcement Learning.}
\texttt{https://arxiv.org/abs/1710.02298}

\bibitem{mnih2013playing} 
Mnih V., Kavukcuoglu K., Silver D., Graves A., Antonoglou I., Wierstra D., Riedmiller M. (2013).
\textit{Playing Atari with Deep Reinforcement Learning.}
\texttt{https://arxiv.org/abs/1312.5602}

\bibitem{mnih2015human} 
Mnih V., Kavukcuoglu K., Silver D., Rusu A., Veness J., Bellemare M., Graves A., Riedmiller M., Fidjeland A., Ostrovski G., Petersen S., Beattie C., Sadik A., Antonoglou I., King H., Kumaran D., Wierstra D., Legg S., Hassabis D. (2015).
\textit{Human-level control through deep reinforcement learning.}
\texttt{https://web.stanford.edu/class/psych209/Readings/ MnihEtAlHassibis15NatureControlDeepRL.pdf}

\bibitem{hasselt2015deep} 
Hasselt H., Guezand A., Silver D. (2015).
\textit{Deep Reinforcement Learning with Double Q-learning.}
\texttt{https://arxiv.org/pdf/1509.06461.pdf}

\bibitem{wang2016dueling} 
Wang Z., Schaul T., Hessel M., Hasselt H., Lanctot M., Freitas N. (2016).
\textit{Dueling Network Architectures for Deep Reinforcement Learning.}
\texttt{https://arxiv.org/pdf/1511.06581.pdf}

\bibitem{schaul2016prioritized} 
Schaul T., Quan J., Antonoglou I., Silver D. (2016).
\textit{Prioritized Experience Replay.}
\texttt{https://arxiv.org/abs/1511.05952}

\bibitem{kingma2017adam} 
P. Kingma D., Ba J. (2017).
\textit{Adam: A Method for Stochastic Optimization.}
\texttt{https://arxiv.org/pdf/1412.6980.pdf}

\bibitem{kingma2017adam} 
Lillicrap T., Hunt J., Pritzel A., Heess N., Erez T., Tassa Y., Silver D., Wierstra D. (2019).
\textit{Continuous Control with Deep Reinforcement Learning.}
\texttt{https://arxiv.org/pdf/1509.02971.pdf}

\bibitem{nguyen2020estimation} 
Nguyen Van Phu C., Farhi N. (2020).
\textit{Estimation of urban traffic state with probe vehicles.}
\texttt{https://arxiv.org/pdf/1811.05394.pdf}

\bibitem{kheterpal2018flow}
Kheterpal N., Parvate K., Wu C., Kreidieh A., Vinitsky E., Bayen A. (2018).
\textit{Flow: Deep Reinforcement Learning for Control in SUMO.}
\texttt{https://flow-project.github.io/papers/Flow\_Deep\_Reinforcement\_Learning \_for\_Control\_in\_SUMO.pdf}

\bibitem{kreidieh2018dissipating}
Kreidieh A., Wu C., Baye A. (2018).
\textit{Dissipating stop-and-go waves in closed and open networks via deep reinforcement learning.}
\texttt{https://flow-project.github.io/papers/08569485.pdf}

\bibitem{vinitsky2018lagrangian}
Vinitsky E., Parvate K., Kreidieh A., Wu C., Bayen A. (2018).
\textit{Lagrangian Control through Deep-RL: Applications to Bottleneck Decongestion.}
\texttt{https://flow-project.github.io/papers/LagrangianBottlenecks.pdf}

\bibitem{vinitsky2018lagrangian}
Wu C., Kreidieh A., Vinitsky E., Bayen A. (2017).
\textit{Emergent Behaviors in Mixed-Autonomy Traffic.}
\texttt{https://flow-project.github.io/papers/wu17a.pdf}

\bibitem{alam2015design}
Alam J., MK P. (2015).
\textit{Design and Analysis of a Two Stage Traffic Light System Using Fuzzy Logic.}
\texttt{https://www.longdom.org/open-access/design-and-analysis-of-a-two-stage -traffic-light-system-using-fuzzy-logic-2165-7866-1000162.pdf}

\bibitem{stevens2016reinforcement}
Stevens M., Yeh C. (2016).
\textit{Reinforcement Learning for Traffic Optimization.}
\texttt{http://cs229.stanford.edu/proj2016spr/report/047.pdf}

\bibitem{genders2019opensource}
Genders W., Razavi S. (2019).
\textit{An Open-Source Framework for Adaptive Traffic Signal Control.}
\texttt{https://arxiv.org/pdf/1909.00395.pdf}

\bibitem{li2016traffic}
Li L., Lv Y., Wang F. (2016).
\textit{Traffic Signal Timing via Deep Reinforcement Learning.}
\texttt{https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=7508798}

\bibitem{gao2017adaptative}
Gao J., Shen Y., Liu J., Ito M., Shiratori N. (2017).
\textit{Adaptive Traffic Signal Control: Deep Reinforcement Learning Algorithm with Experience Replay and Target Network.}
\texttt{https://arxiv.org/pdf/1705.02755.pdf}

\bibitem{gao2017adaptative}
Gao J., Shen Y., Liu J., Ito M., Shiratori N. (2017).
\textit{Adaptive Traffic Signal Control: Deep Reinforcement Learning Algorithm with Experience Replay and Target Network.}
\texttt{https://arxiv.org/pdf/1705.02755.pdf}

\bibitem{liang2019deep}
Liang X., Du X., Wang G., Han Z. (2019).
\textit{A Deep Reinforcement Learning Network for Traffic Light Cycle Control.}
\texttt{https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=\&arnumber=8600382}

\bibitem{wei2018intellilight}
Wei H., Zheng G., Yao H., Li Z. (2018).
\textit{IntelliLight: A Reinforcement Learning Approach for Intelligent Traffic Light Control.}
\texttt{https://dl.acm.org/doi/pdf/10.1145/3219819.3220096}

\bibitem{vidali2019deep}
Vidali A., Crociani L., Vizzari G., Bandini S. (2019).
\textit{A Deep Reinforcement Learning Approach to Adaptive Traffic Lights Management.}
\texttt{http://ceur-ws.org/Vol-2404/paper07.pdf}

\bibitem{alemzadeh2020adaptative}
Alemzadeh S., Moslemi R., Sharma R., Mesbahi M. (2020).
\textit{Adaptive Traffic Control with Deep Reinforcement Learning: Towards State-of-the-art and Beyond.}
\texttt{https://arxiv.org/pdf/2007.10960.pdf}

\bibitem{pol2016coordinated}
Pol E., Oliehoek F. (2016).
\textit{Coordinated Deep Reinforcement Learners for Traffic Light Control.}
\texttt{http://www.v6.fransoliehoek.net/docs/VanDerPol16LICMAS.pdf}

\bibitem{wei2019presslight}
Wei H., Chen C., Zheng G., Wu K., Gayah V., Xu K., Li Z. (2019).
\textit{PressLight: Learning Max Pressure Control to Coordinate Traffic Signals in Arterial Network.}
\texttt{http://personal.psu.edu/hzw77/publications/presslight-kdd19.pdf}

\bibitem{wei2019colight}
Wei H., Xu N., Zhang H., Zheng G., Zang X., Chen C., Zhang W., Zhu Y., Xu K., Li Z. (2019).
\textit{CoLight: Learning Network-level Cooperation for Traffic Signal Control.}
\texttt{http://faculty.ist.psu.edu/jessieli/Publications/2019-CIKM-colight.pdf}

\bibitem{chen2020toward}
Chen C., Wei H., Xu N., Zheng G., Yang M., Xiong Y., Xu K., Li Z. (2020).
\textit{Toward A Thousand Lights: Decentralized Deep Reinforcement Learning for Large-Scale Traffic Signal Control.}
\texttt{https://ojs.aaai.org/index.php/AAAI/article/view/5744/5600}

\bibitem{zhang2020using}
Zhang R., Ishikawa A., Wang W., Striner B., Tonguz O. (2020).
\textit{Using Reinforcement Learning with Partial VehicleDetection for Intelligent Traffic Signal Control.}
\texttt{https://arxiv.org/pdf/1807.01628.pdf}

\bibitem{zhang2019partially}
Zhang R., Leteurtre R., Striner B., Alanazi A., Alghafis A., Tonguz O. (2019).
\textit{Partially Detected Intelligent Traffic Signal Control: Environmental Adaptation.}
\texttt{https://arxiv.org/pdf/1910.10808.pdf}

\bibitem{genders2018evaluating}
Genders W., Razavi S. (2018).
\textit{Evaluating reinforcement learning state representations for adaptive traffic signal control.}
\texttt{https://www.sciencedirect.com/science/article/pii/S1877050918303582/pdf? md5=f7c89fc22054a24b0b7541772eb4da10\&pid=1-s2.0-S1877050918303582-main.pdf}

\bibitem{touhbi2017adaptative}
Touhbi S., Babram M., Nguyen-Huu T., Marilleau N., Hbid M., Cambier C., Stinckwich S. (2017).
\textit{Adaptive Traffic Signal Control: Exploring Reward Definition For Reinforcement Learning.}
\texttt{https://www.sciencedirect.com/science/article/pii/S1877050917309912/pdf? md5=2045e01880ec7708d9a3faff83a2f80d\&pid=1-s2.0-S1877050917309912-main.pdf}

\bibitem{wei2020survey}
Wei H., Zheng G., Gayah V., Li Z. (2020).
\textit{A Survey on Traffic Signal Control Methods.}
\texttt{https://arxiv.org/pdf/1904.08117.pdf}

\bibitem{dlr2021sumo}
German Aerospace Center DLR. (2001-2021).
\textit{SUMO User Documentation.}
\texttt{https://sumo.dlr.de/docs/index.html}

\bibitem{krizhevsky2012imagenet}
Krizhevsky A., Sutskever I., Hinton G. (2012).
\textit{ImageNet Classification with Deep Convolutional Neural Networks.}
\texttt{https://papers.nips.cc/paper/2012/file/c399862d3b9d6b76c8436e924a68c45 b-Paper.pdf}

\bibitem{varaiya2013max}
Varaiya P. (2013).
\textit{Max pressure control of a network of signalized intersections.}
\texttt{https://www.researchgate.net/publication/259138901\_Max\_pressure\_contro l\_of\_a\_network\_of\_signalized\_intersections}

\bibitem{gershenson2004self}
Gershenson C. (2004).
\textit{Self-Organizing Traffic Lights.}
\texttt{https://arxiv.org/pdf/nlin/0411066.pdf}

\end{thebibliography}

\noindent\rule{\textwidth}{1pt}
\\

Cite as: Ducrocq R. (2021). 
\textit{Deep Reinforcement Q-Learning for Intelligent Traffic Signal Control with Partial Detection.}
\texttt{https://github.com/romainducrocq/DQN-ITSCwPD}